\documentclass[journal]{IEEEtran}
  \usepackage{graphicx}
  \usepackage{caption}
  \usepackage{hyperref}

  \begin{document}
  \title{Journal 10}
  \author{Thomas Hastings}% <-this % stops a space
  
  \markboth{Thomas Hastings, CS6000}%
  {Shell}
  \maketitle
  
  \begin{abstract}
  This journal is for homework in Dr. Boult's CS6000 course.
  \end{abstract}
  
  % Note that keywords are not normally used for peerreview papers.
  \begin{IEEEkeywords}
  Homework
  \end{IEEEkeywords}
  
  
  \section{Reflection}
  % Some journals put the first two words in caps:
Over all I enjoyed this class. I seemed to pick up a nugget of information from each lecture. 
\subsection{Like}
I am thankful to have learned about Zotero. It has saved a lot of time with other papers and other research that I am working on. I also enjoyed learning about conferences and what makes a good conference versus a bad conference and how authors are ranked by the H-Index. I also learned through the course of writing the survey paper that I really was not interested in my topic. I have worked with my advisor and we have come up with a new road map for my studies in a direction that I believe makes more sense. 

\subsection{Dislike}
At first I went about writing the survey paper backwards by picking sources first and then trying to formulate a story based on my sources. That did not work. I had to go back and formulate the story I wanted to tell and then survey sources to identify the papers that helped tell the story. I did not feel that I had the depth of experience to write a survey paper but I am glad I attempted it.

  
  % that's all folks
  \end{document}
  